---
title: "Homework 13"
author: "Kelsey Conaway"
date: "December 4, 2018"
output: pdf_document
---
STAT 5193
R Markdown

Question 1.a
```{r}
library(readxl)
setwd("C:/Users/Kelsey/Documents/R Projects/")
StudentData <- read_excel("Data Sets/StudentData.xlsx")


t.test(StudentData$HSClass~StudentData$Snapchat,conf.level = 0.95)
```
The test rendered a CI of (-344.08,31.101) and since 0 is in the interval this indicates there's no significant difference in the mean high school class size of those who Snapchat and those who don't.

Question 1.b
```{r}
boxplot(StudentData$HSClass~StudentData$Snapchat)
```

Question 1.c
```{r}
t.test(StudentData$HSClass~StudentData$Snapchat,
       alternative = "less")
```
The p-value of 0.04938 would indicate that there is significant evidence that the mean high school class size is smaller for those who do not have Snapchat than those who do.


Question 1.d
```{r}
t.test(StudentData$HSClass~StudentData$Snapchat,
       conf.level=0.9)
```
The CI (-312.39,-0.596) does not include 0 which would indicate that there is significant evidence to say that the average class size is different for those who use Snapchat and those who don't at the 90% confidence level.

Question 2.a
```{r}
plot(USArrests$Assault,USArrests$Murder)

model<-lm(Murder~Assault, data=USArrests)
abline(model)
```
Question 2.b

summary(model) output the following values:

Estimate          Std.Error     t       value   Pr(>|t|)  
USArrests$Assault 0.041909   0.004507   9.298  2.6e-12 ***

The p-value 2.6 ^(-12) indicates that the variable are not independent of one another.

Question 2.c
```{r}
new<-data.frame(Assault=151)
predict.lm(model,new,interval = "prediction")
```

Question 2.d
```{r}
plot(USArrests$Assault,USArrests$Murder)
abline(model)

predict_int<- predict(model,
                      new=data.frame(Assault=50:400),
                      interval = "prediction", 
                      level = 0.95)

x<-seq(50,400,by=1)


lines(x,predict_int[,3])
lines(x,predict_int[,2])
```
```{r}
 
```

