---
title: "Homework 12"
author: "Kelsey Conaway"
date: "November 30, 2018"
output: pdf_document
---
STAT 5093
R Markdown

Question 1.a
```{r}
library(readxl)
SData <- read_excel("~/R Projects/Data Sets/StudentData.xlsx")

library(vcd)
gp_student<-table(SData$Gender,SData$Pinterest)
gp_student
```

Question 1.b
```{r}
p_gp<-prop.table(margin.table(gp_student,1:2),1)
p_gp
```

Question 1.c 
```{r}
resid<-resid(chisq.test(gp_student))
resid[,2]
```
There were more female and less male Pinterest users than expected 

Question 1.d and 1.e
```{r}
barplot(t(gp_student),
        beside=TRUE,
        names=c("Female","Male"),
        col= c("grey","red","grey","red"),
        main="Pinterest Depends on Gender (p=0.03397)")

#fisher.test(gp)

legend("topright",
       inset=0.05,
       title="Pinterest",
       legend= c("No","Yes"),
       fill = c("grey","red"))
```

Question 2
```{r}
survivors <- apply(Titanic,c(1,4),sum)
mosaic(survivors, legend=T, gp=shading_max)
```
The p-value of <2.22^(-16) would indicate that survival depended on class


Question 3
```{r}
gender<-apply(Titanic,c(2,4),sum)
chisq.test(gender)
```
The p-value of <2.2^(-16) indicates that survival rate significantly depended on gender.

Question 4
```{r}
age <- apply(Titanic,c(3,4),sum)
chisq.test(age)
```
The p-value of 7.725^(-6) indicates that survival rate significantly depended on age.